
\begin{question}
Determine whether each of the following codes is uniquely decodable (UD), prefix, instantaneous, or near instantaneous:
\begin{enumerate}
\item \{0,01,11,111\}
\item \{0,01,110,111\}
\item \{0,10,110,111\}
\item \{1,10,110,111\}
\end{enumerate}
\end{question}

\begin{solution}

\begin{table}[h]
\renewcommand{\arraystretch}{1.3}
\centering
\begin{tabular}{c|c|c|c|c}
\hline
 Code & UD  & Prefix  & Intantaneous & Near-instantaneous \\
\{0,01,11,111\} & F & F & F & T \\
\{0,01,110,111\} & F & F & F & T \\
\{0,10,110,111\} & F & F & F & F \\
\{1,10,110,111\} & F & F & F & F \\
\hline
\end{tabular}
\end{table}
\end{solution}

\begin{question}
An alphabet of 7 symbols, had code lengths of 2, 2, 3, 3, 3, 3, \& 3 bits. Is this code uniquely decodable? Why?
\end{question}
\begin{solution}
No. \\
Reasons: \\
$K = - \sum_{i=1}^{l} 2^{-l} = 2 \times 2^{-2} + 5 \times 2^{-3} = 1.125$ \\
$ \therefore \text{ not UD } (K>1).$ \\

\end{solution}


\begin{question}
What the largest number is of symbols that can be coded using a ternary (i.e. 3 symbols) code, while the code length of each symbol does not exceed 3? Why?
\end{question}
\begin{solution}
The largest number is 27.\\
Reasons: using a 3 symbols for each code results in $3^3$ variants. 
\end{solution}



\begin{question}
14 symbols are coded using a ternary (i.e. 3) code. The code lengths are 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 3, \& 3. Is this code uniquely decodable? Why?
\end{question}
\begin{solution}
Uniquely decodable. \\
Reasons: \\
$K = - \sum_{i=1}^{l} 3^{-l} = 6 \times 3^{-2} + 8 \times 3^{-3} = 0.963$ \\
$\therefore \text{ is decodable } (K<1)$.
\end{solution}


\begin{question}
An alphabet of 7 symbols, had code lengths of 2, 2, 3, 3, 3, 3, \& 3 bits. Is this code uniquely decodable? Why?
\end{question}
\begin{solution}
Not UD. \\
Reasons: \\
$K = - \sum_{i=1}^{l} 2^{-l} = 2 \times 2^{-2} + 5 \times 2^{-3} = 1.125$ \\
$ \therefore \text{ not UD } (K>1).$ \\

\end{solution}


\begin{question}
Using Kraft’s Inequality, check the decidability of the
following code table. Next, check the code table. Is the
code decodable? Why? Calculate the entropy, the average
code length, and the redundancy
\begin{table}[h]
\renewcommand{\arraystretch}{1.3}
\centering
\begin{tabular}{c|c|c}
\hline
Symbol & Probability & Code \\
a & 0.125 & 0 \\
b & 0.125 & 10 \\
c & 0.25 & 110 \\
d & 0.5 & 101 \\
\hline
\end{tabular}
\end{table}

\end{question}
\begin{solution}
Kraft’s inequality result: \\
$K = - \sum_{i=1}^{l} 2^{-l} = 2 \times 2^{-3} + 2^{-2} + 2^{-1} = 1$ \\
Decodability based on Kraft’s inequality: UD ($K\leq1$).\\
Is the code decodable? \\ 
No. \\
Why? \\
Dangling Suffixes = \{1,10,0\} which includes codes \{10,0\} from the original codes.\\
Average Code Length = 2.625 bits/symbol. \\
Redundancy = 0.875 bits/symbol.
\end{solution}


\begin{question}
Assume a 5-symbol alphabet \{A, B, C, D, E\}. Build a prefix code for the symbols. Then code the sequence: CBABAA.
\end{question}
\begin{solution}
\begin{table}[h]
\renewcommand{\arraystretch}{1.3}
\centering
\begin{tabular}{c|c|c|c|c|c}
\hline
Symbol & A & B & C & D & E \\
Code & 0 & 10 & 110 & 1110 & 1111 \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\renewcommand{\arraystretch}{1.3}
\centering
\begin{tabular}{c|c|c|c|c|c|c}
\hline
Symbol & C & B & A & B & A & A \\
Code & 110 & 10 & 0 & 10 & 0 & 0 \\
\hline
\end{tabular}
\end{table}

\end{solution}

